A linear inside-outside algorithm for correcting sequencing errors in structured RNA sequences

### 2012-10-07 Recomb/conclusion_RECOMB.tex
conclusion

By combining these two approaches,  the 
mutational landscape exploration and the pseudo energy model,
 into \texttt{RNApyro}, we obtained a tool to predict the position and 
correct randomly mutated 5s rRNA sequences. 
As presented in Sec.~\ref{sec:results},
we observe that the models
with larger weights on the
isostericity seems to hold a higher accuracy on the estimation of errors.
Importantly, the implementation is fast enough for practical applications.

>>>>

By combining these two approaches,  the 
mutational landscape exploration and the pseudo energy model,
 into \texttt{RNApyro}, we created a tool predicting the positions
 yielding sequencing error and their correct value.
We validated our model with the 5s rRNA,
as presented in Sec.~\ref{sec:results}.
We observed that the models
with larger weights on the
isostericity seems to hold a higher accuracy on the estimation of errors.
Importantly, the implementation is fast enough for practical applications.
